Pulmonary acini exhibit complex changes during postnatal rat lung development

### 2021-01-18 manuscript.tex
Implement tweaks as suggested by Johannes [ci skip]
This build is based on
https://github.com/habi/acinar-analysis-manuscript/commit/ca2252149052d2112e9155e62f10bf5e05075b68.

This commit was created by the following CI build and job:
https://github.com/habi/acinar-analysis-manuscript/commit/ca2252149052d2112e9155e62f10bf5e05075b68/checks
https://github.com/habi/acinar-analysis-manuscript/runs/493813332

A preprint of this manuscript is available on \emph{bioRxiv} with the DOI \href{https://doi.org/10.1101/786681}{10.1101/786681} and is under revision in the \href{https://journals.physiology.org/journal/ajplung}{\emph{American Journal of Physiology - Lung Cellular and Molecular Physiology}}.
The manuscript \href{https://github.com/habi/acinar-analysis-manuscript/compare/d6fc17bd66bdca5cbff30d53e1dbc02d5351609b...d20ffa7aad63d66cb17d8ab2ec0f577c1f74023a}{has been updated} since the first round of review.

This manuscript
(\href{https://habi.github.io/acinar-analysis-manuscript/v/d20ffa7aad63d66cb17d8ab2ec0f577c1f74023a/}{permalink})
was automatically generated
from \href{https://github.com/habi/acinar-analysis-manuscript/tree/d20ffa7aad63d66cb17d8ab2ec0f577c1f74023a}{habi/acinar-analysis-manuscript@d20ffa7}
on January 18, 2021.

@@

\begin{itemize}
\item
  \textbf{David Haberthür}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3388-9187}{0000-0003-3388-9187}
  · \href{mailto:haberthuer@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(d20ffa7)}{haberthuer@ana.unibe.ch}
  · \includegraphics{images/github.svg}
  \href{https://github.com/habi}{habi}
  · \includegraphics{images/twitter.svg}
  \href{https://twitter.com/habi}{habi}
  Institute of Anatomy, University of Bern, Switzerland
\item
  \textbf{Eveline Yao}
  Institute of Anatomy, University of Bern, Switzerland
\item
  \textbf{Sébastien F. Barré}
  Institute of Anatomy, University of Bern, Switzerland
\item
  \textbf{Tiziana P. Cremona}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-0061-9578}{0000-0003-0061-9578}
  Institute of Anatomy, University of Bern, Switzerland
\item
  \textbf{Stefan A. Tschanz}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3880-4437}{0000-0003-3880-4437}
  Institute of Anatomy, University of Bern, Switzerland
\item
  \textbf{Johannes C. Schittny}✉
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-4025-3961}{0000-0003-4025-3961}
  · \href{mailto:schittny@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(d20ffa7)}{schittny@ana.unibe.ch}
  Institute of Anatomy, University of Bern, Switzerland
\end{itemize}

>>>>

A preprint of this manuscript is available on \emph{bioRxiv} with the DOI \href{https://doi.org/10.1101/786681}{10.1101/786681} and is under revision in the \href{https://journals.physiology.org/journal/ajplung}{\emph{American Journal of Physiology - Lung Cellular and Molecular Physiology}}.
The manuscript \href{https://github.com/habi/acinar-analysis-manuscript/compare/d6fc17bd66bdca5cbff30d53e1dbc02d5351609b...ca2252149052d2112e9155e62f10bf5e05075b68}{has been updated} since the first round of review.

This manuscript
(\href{https://habi.github.io/acinar-analysis-manuscript/v/ca2252149052d2112e9155e62f10bf5e05075b68/}{permalink})
was automatically generated
from \href{https://github.com/habi/acinar-analysis-manuscript/tree/ca2252149052d2112e9155e62f10bf5e05075b68}{habi/acinar-analysis-manuscript@ca22521}
on January 18, 2021.

@@

\begin{itemize}
\item
  \textbf{David Haberthür}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3388-9187}{0000-0003-3388-9187}
  · \href{mailto:haberthuer@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(ca22521)}{haberthuer@ana.unibe.ch}
  · \includegraphics{images/github.svg}
  \href{https://github.com/habi}{habi}
  · \includegraphics{images/twitter.svg}
  \href{https://twitter.com/habi}{habi}
  Institute of Anatomy, University of Bern, Switzerland
\item
  \textbf{Eveline Yao}
  Institute of Anatomy, University of Bern, Switzerland
\item
  \textbf{Sébastien F. Barré}
  Institute of Anatomy, University of Bern, Switzerland
\item
  \textbf{Tiziana P. Cremona}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-0061-9578}{0000-0003-0061-9578}
  Institute of Anatomy, University of Bern, Switzerland
\item
  \textbf{Stefan A. Tschanz}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3880-4437}{0000-0003-3880-4437}
  Institute of Anatomy, University of Bern, Switzerland
\item
  \textbf{Johannes C. Schittny}✉
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-4025-3961}{0000-0003-4025-3961}
  · \href{mailto:schittny@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(ca22521)}{schittny@ana.unibe.ch}
  Institute of Anatomy, University of Bern, Switzerland
\end{itemize}
